What is essential?

### 2016-03-17 paper/presentation/presentation.tex
add metamodel
add stuff

@@

\begin{Slide}{28 atributes of the metamodel (see paper appendix)}
\fontsize{6}{6.5}\selectfont
\begin{tabular}{l l}
\textbf{\textit{Attributes}} & \textbf{\textit{Definition}}  \\
\input{../proceedings/attribute-defs.tex}
\end{tabular}
\end{Slide}

@@

\begin{Slide}{Essentiality Definition}
\begin{itemize}
\item If an ''essentiality threshold'' is chosen at $N/2$ then \\ only the $9$ concepts from row $n = 7$ and below are considered ''non-essential''
\item \Alert{More than 90\% of the 92 metamodel concepts have a majority of the subjects that use them and agree upon their definitions} 
\item Each concept has at least one subject that uses it and agrees with its definition. 
\end{itemize}

@@

\begin{itemize} 
\item Future Work
\begin{itemize} 
\item More subjects for increased external validity
\item More questions on missing and alternative concepts
\end{itemize}
\end{itemize}
\end{Slide}

>>>>

\begin{Slide}{The base classes of the reqT metamodel}
\includegraphics[width=0.9\textwidth]{img/metamodel}
\end{Slide}

@@

\begin{Slide}{28 attributes of the metamodel (see paper appendix)}
\fontsize{6}{6.5}\selectfont
\begin{tabular}{l l}
\textbf{\textit{Attributes}} & \textbf{\textit{Definition}}  \\
\input{../proceedings/attribute-defs.tex}
\end{tabular}
\end{Slide}

@@

\begin{Slide}{Essentiality Definition}
\begin{itemize}
\item If an ''essentiality threshold'' is chosen at $N/2$ then \\ only the $9$ concepts from row $n = 7$ and below are considered ''non-essential''
\item \Alert{More than 90\% of the 92 metamodel concepts have a majority of the subjects that use them and agree upon their definitions} 
\item Each concept has at least one subject that uses it and agrees with its definition. 
\end{itemize}
\end{Slide}

\begin{Slide}{Omissions}
%\vspace{0.1cm}
%\fontsize{9}{10}\selectfont 
\Alert{Missing Concepts} according to subjects:\\
S01: \Emph{or}, \\
S02: bug, threshold, \\
S04: role, problem, motivates, and, \Emph{or}, pattern, submodel, \\
S06: plug-in, informalism, \\
S07: full sentence, \\
S09: satisfaction, satisfies, customer, \\
S11: system-of-interest, verification, validation, \\
S13: context.

@@

\begin{itemize} 
\item Future Work
\begin{itemize} 
\item Increase validity
\item Investigate omissions
\end{itemize}
\end{itemize}
\end{Slide}
